### 2017-01-11 papers.tex
Adds comment to ind_009

% =============================================================================
\section{\texttt{IND\_008} - Discovering decision knowledge from web log
portfolio for managing classroom processes by applying decision tree and data
cube technology}

@@

>>>>

% =============================================================================
\section{\texttt{IND\_008} - Discovering Decision Knowledge From Web Log
Portfolio For Managing Classroom Processes By Applying Decision Tree And Data
Cube Technology}

@@

% =============================================================================
\section{\texttt{IND\_009} - Predicting Performance From Test Scores Using
Backpropagation and Counterpropagation}

Paper is~\cite{ind_009}. Neural Networks are used to predict students grades
from placement test responses. This paper was found from~\cite{ind_007}.

Backpropagation and Counterpropagation are two types of neural networks that
are trained in different ways. This paper uses both types of networks to
predict students grades. The data set used in this paper is small, but more
data is generated from it. The data refers to placement tests for a course on
Calculus I at West University Boulevard in Florida.

The initial data set is small. It contains 116 entries. Each entry has 25
features, which although not specified in the paper, are stated to be results
from placement tests. Each entry also contains the final grade of the student,
from \textit{A} to \textit{D} stating a different level of approval, and
\textit{F} when a student failed. Because the data is small, some data has been
generated.

The networks contains 25 inputs, for the features, and 5 outputs, for each
grade. An output of \textit{A} will be a vector of the form $ [1, -1, -1, -1,
-1] $, for \textit{B} it will be $ [-1, 1, -1, -1, -1] $, and so on. The
networks contain a single hidden layer which number of units varies for
different trainings. The number of units are 15, 20, 25, and 30 for different
tests.

It is shown how the networks are trained and are able to achieve correctly
classify students, given their input data. It seems that an optimal number of
units in the hidden layer is 25. Some networks achieve 80\% of correctly
classified instances for a pure dataset. Training networks with generated
datasets is yields greater correctly classified percentages between 90\% and
100\%.

Although the results shown are very good, the paper doesn't go into detail
about the inputs of the networks. It is important to know to format of the data
of the students placement tests, how the data was pre-processed, and into what
was it pre-processed. Like this, the paper leaves to much to speculation. It
would also be nice to see how these methods are applied in other courses.

The paper presents the hypothesis that neural networks are good for predicting
student's performance based on existing placement tests for a given course on
Calculus I. It then shows how data is taken and used to generate more data. The
networks are trained and are able to achieve great results.

This paper is important because it is prof that neural networks can be used to
classify student performance. It is also important because it shows a useful
and successful tasks in the world of~\gls{edm}.

Ideas from this paper may be used for later study.

This paper only has four references, and all of them are related with Neural
Networks. Those references might came in handy if work is to be done in Neural
Networks, but not for data mining in~\gls{lms}.
